Supplementary Materials to ``Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic''

### 2021-09-02 write-up/covid-supplement-writeup.tex
So close - just final edits

In this section, we describe the two mean-imputation methods.
\subsection{Model 1}

@@

For simplicity, we list the priors used in STAN below:
\begin{itemize}
  \item \code{beta $\sim$ Normal(1.5, 1) T[0,];}
  \item \code{gamma $\sim$ normal(0.3, 0.5) T[0,];}
  \item \code{sigma $\sim$ normal(0.4, 0.5) T[0,];}
  \item \code{phi\_inv $\sim$ exponential(5);}
  \item \code{i0 $\sim$ normal(0, 10);}
  \item \code{e0 $\sim$ normal(0, 10);}
  \item \code{eta $\sim$ normal(1, 1) T[0,];}
  \item \code{eta\_two $\sim$ normal(1, 1) T[0,];}
  \item \code{eta\_three $\sim$ normal(1, 1) T[0,];}
  \item \code{nu $\sim$ exponential(1./5);}
  \item \code{nu\_two $\sim$ exponential(1./5);}
  \item \code{nu\_three $\sim$ exponential(1./5);}
  \item \code{xi\_raw $\sim$ beta(1, 1);}
  \item \code{phi = 1/phi\_inv;}
  \item \code{xi = xi\_raw + 0.5;}
\end{itemize}
where \code{beta, eta, eta\_two, eta\_three} refer to the four values that form the time-varying parameter $\beta_t$ when combined with \code{xi, eta, eta\_two, eta\_three} in the SEIR model as described in Section~\ref{section:modelbased}.

>>>>

Table~\ref{tab:comparison} demonstrates minimal bias in the Facebook symptom survey with respect to symptom distributions.

 \begin{table}[!th]
 \centering
 \begin{tabular}{c | c c c | c}
 & \multicolumn{3}{c}{Facebook} & Random \\ \cline{2-4}
 & Lower CI & Estimate & Upper CI & Estimate \\ \hline
 Fever &  0.017 & 0.020 & 0.024 & 0.018 \\
 Cough &  0.142 & 0.148 & 0.154 & 0.149 \\
 Shortness & 0.058 & 0.060 & 0.062 & 0.062 \\ \hline
 \end{tabular}
 \caption{Comparison of Facebook survey and random sample}
 \label{tab:comparison}
 \end{table}

Next, we describe the two mean-imputation methods.
\subsection{Model 1}

@@

For simplicity, we list the priors used in STAN below:
\begin{itemize}
  \item \code{beta $\sim$ Normal(1.5, 1) T[0,];}
  \item \code{gamma $\sim$ normal(0.3, 0.5) T[0,];}
  \item \code{sigma $\sim$ normal(0.4, 0.5) T[0,];}
  \item \code{phi\_inv $\sim$ exponential(5);}
  \item \code{i0 $\sim$ normal(0, 10);}
  \item \code{e0 $\sim$ normal(0, 10);}
  \item \code{eta $\sim$ normal(1, 1) T[0,];}
  \item \code{eta\_two $\sim$ normal(1, 1) T[0,];}
  \item \code{eta\_three $\sim$ normal(1, 1) T[0,];}
  \item \code{nu $\sim$ exponential(1./5);}
  \item \code{nu\_two $\sim$ exponential(1./5);}
  \item \code{nu\_three $\sim$ exponential(1./5);}
  \item \code{xi\_raw $\sim$ beta(1, 1);}
  \item \code{phi = 1/phi\_inv;}
  \item \code{xi = xi\_raw + 0.5;}
\end{itemize}
where \code{beta, eta, eta\_two, eta\_three} refer to the four values that form the time-varying parameter $\beta_t$ when combined with \code{xi, eta, eta\_two, eta\_three} in the SEIR model as described in Section~\ref{section:modelbased}. Following~\cite{Song2020}, we employ Runge-Kutta (RK4) approximations for discretization.
